May I Ask Where You Have Been, Photon?

### 2021-11-19 article.tex
rearrange figures and write more on double slit experiment

\documentclass{article}

@@

\usepackage{svg}
\usepackage{subfig}

\newcommand{\Q}{\medskip\bfseries Q: }
\newcommand{\A}{\par\textbf{A:} \normalfont}

@@

\begin{figure}[ht]
	\includesvg[width=\linewidth]{figures/interferometer1.svg}
	\caption{Simple Mach Zehnder interferometer}
	\label{fig:interferometer1}
\end{figure}

Quantum physics describes physical interactions that happen at the atomic and
sub-atomic levels, and underpins the foundation for most of modern technology.
However, physicists are still unsure how to use standard quantum theory to 
answer the following question: what path did a photon take through an 
interferometer before quantum measurement was performed?  A recent experiment 
conducted by A. Danan and colleagues at Tel Aviv University in Israel sheds 
light on how difficult it is exactly to answer this question in any but the 
simplest of situations.

In classical physics, a particle travelling between two points has a single
trajectory, which can be calculated by specifying its state at either endpoint
of the trajectory. On the other hand, in quantum physics, the trajectory a
particle takes between two measurements is a weighted sum, or superposition, of
every path it could have taken between the two measurements. This gives rise to
the phenomenon of a particle interfering with itself before being measured, as
demonstrated by experiments like the single-particle version of Young's double
slit experiment.

In the double slit experiment (as performed by Thomas Young), a beam of light 
is passed through two closely spaced slits and projected onto the screen.  
According to classical wave theory, the intensity of light detected at the 
screen is given by the intensity of the incident waves as well as their 
relative phases. Because of the different different distances traveled by 
different wavefronts, phase difference arise, in turn giving rise to an 
interference pattern on the screen, as shown in figure 
\label{fig:uncollimated}.

\begin{figure}
	\fbox{\subfloat[Standard 
	setup]{\includesvg[width=0.5\linewidth]{figures/double-slit.svg}}\label{fig:uncollimated}}
	\fbox{\subfloat[Collimated 
	beams]{\includesvg[width=0.5\linewidth]{figures/collimated-double-slit.svg}}\label{fig:collimated}}
	\caption{Young's double slit interference experiment}
	\label{fig:double-slit}
\end{figure}

Another apparatus that can demonstrate single-particle interference is the
Mach-Zehnder interferometer, which consists of a light source and a detector 
along with two beam splitters (basically half-silvered mirrors) and two 
mirrors, arranged as shown in [figure]. In the classical version of the 
experiment, the light source emits a continuous beam of light, which partly 
passes through the the first beam splitter, and is then reflected by the two 
mirrors to meet at the second beam splitter. Reflection at an interface between 
vacuum and the silvered side of a mirror causes a phase change through a purely 
classical phenomenon, which means that the beams coming out of the second beam 
splitter combine totally constructively on one side, and totally destructively 
on the other, in analogy to the bright and dark bands in the classical double 
slit experiment. Extending the analogy to the double-slit experiment, if the 
light source in the Mach-Zehnder interferometer is tuned to a low-enough 
intensity that single photons emitted can be resolved by the detector, it is 
found that the photon arrives at the detector 100\% of the time, demonstrating 
the phenomenon of a particle interfering with itself. Of course, if we remove 
the second beam splitter, there is a 50\% chance that the photon will show up 
in our detector, and a 50\% chance that it will come out of the other branch of 
the interferometer.

Here, we attempt to answer the titular question using the "common sense" 
approach amateur science enthusiasts and undergraduate physics students are 
familiar with:

\Q May I Ask Where You Have Been, Photon?

>>>>

\documentclass{article}
\pdfsuppresswarningpagegroup=1

@@

\usepackage{svg,subfig,framed}
\usepackage[a4paper, total={6in, 8in}]{geometry}

\newcommand{\Q}{\bfseries Q: }
\newcommand{\A}{\par\textbf{A:} \normalfont}

@@

\begin{figure}[ht]
	\subfloat[Standard 
	setup]{\fbox{\includesvg[width=0.5\linewidth]{figures/double-slit.svg}}\label{fig:uncollimated}}
	\hspace*{\fill}
	\subfloat["Which-way" experiment
	]{\fbox{\includesvg[width=0.5\linewidth]{figures/collimated-double-slit.svg}}\label{fig:collimated}}
	\caption{Young's double slit interference experiment}
	\label{fig:double-slit}
\end{figure}

Quantum physics describes physical interactions that happen at the atomic and
sub-atomic levels, and underpins the foundation for most of modern technology.
However, physicists are still unsure how to use standard quantum theory to 
answer the following question: what path did a photon take through an 
interferometer before quantum measurement was performed?  A recent experiment 
conducted by A. Danan and colleagues at Tel Aviv University in Israel sheds 
light on how difficult it is to answer this question in any but the simplest of 
situations.

In classical physics, a particle travelling between two points has a single
path, which can be calculated by specifying its state at either endpoint. On 
the other hand, in quantum physics, the trajectory a particle takes between two 
measurements is a weighted sum, or superposition, of every path it could have 
taken between the two measurements. This gives rise to the phenomenon of a 
particle interfering with itself before being measured, as demonstrated by 
experiments like the single-particle version of Young's double slit experiment.

In the classical double slit experiment, a beam of light is passed through two 
closely spaced slits and projected onto a screen. Because of the wave nature of 
light, different distances travelled by different wavefronts give rise to phase 
differences at the screen, causing an interference pattern to appear, as 
illustrated in figure~\ref{fig:uncollimated}. This is similar to interference 
between ripples in a pond, creating zones of zero displacement where crests and 
troughs overlap.

In the modern version of this experiment, the continuous light source is 
replaced by a light source emitting individual particles, and a photosensitive 
plate is used as the screen. Over time, the same interference pattern appears 
on the photosensitive plate as in the classical experiment. This implies that 
individual particles undergo wave-like interference \textit{with themselves}, 
begging the question:

\begin{framed}
\Q Where have you been, photon?

\A Because the particle underwent wave-like interference with itself, it can be 
	said that it took \textit{all possible paths} between the light source 
	and the screen.  However, because it was not observed at any point 
	between the source and the screen, a common position is to claim that
	\textit{one cannot say} where the photon has been.
\end{framed}

One way to try to ascertain where each photon is coming from (in a so-called 
"which-way" experiment) is to insert a lens after each slit, as shown in 
figure~\ref{fig:collimated}.  Each lens only collimates the photons that arrive 
through the corresponding slit, causing the interference pattern to be replaced 
by two distinct spots. It would then seem safe to assume that a photon detected 
in the a spot on the screen must have travelled through the corresponding slit.  
It does not seem possible that a photon detected in, say, the upper spot would 
have gone through the lower lens. It is this seemingly safe assertion that is 
called into question by the Tel-Aviv experiment.

In their experiment, Danan and collagues use the Mach-Zehnder interferometer, 
used by Danan and colleagues in their experiment.  The Mach Zehnder 
interferometer consists of a light source and a detector along with two beam 
splitters (basically half-silvered mirrors) and two mirrors, arranged as shown 
in figure~\ref{fig:interferometer1}. In the classical version of the 
experiment, the light source emits a continuous beam of light, which partly 
passes through the the first beam splitter, and is then reflected by the two 
mirrors to meet at the second beam splitter. Reflection at an interface between 
vacuum and the silvered side of a mirror causes a phase change through a purely 
classical phenomenon, which means that the beams coming out of the second beam 
splitter combine totally constructively on one side, and totally destructively 
on the other, in analogy to the bright and dark bands in the classical double 
slit experiment. Extending the analogy to the double-slit experiment, if the 
light source in the Mach-Zehnder interferometer is tuned to a low-enough 
intensity that single photons emitted can be resolved by the detector, it is 
found that the photon arrives at the detector 100\% of the time, demonstrating 
the phenomenon of a particle interfering with itself. Of course, if we remove 
the second beam splitter, there is a 50\% chance that the photon will show up 
in our detector, and a 50\% chance that it will come out of the other branch of 
the interferometer.

\begin{figure}
	\includesvg[width=\linewidth]{figures/interferometer1.svg}
	\caption{Simple Mach Zehnder interferometer}
	\label{fig:interferometer1}
\end{figure}

Again, we can answer titular question using "common sense" approach amateur 
science enthusiasts and undergraduate physics students are familiar with:

\medskip\Q May I ask where you have been, photon?
